---
title: "Behavioral Economic Analysis of Pigeons' Token Accumulation and Reinforcer Demand"
subtitle: "Reproducible analysis for Wan, Tan, & Hackenberg (2026), *Journal of the Experimental Analysis of Behavior*"
author:
  - name: "Haoran Wan"
    orcid: "0000-0002-3434-3146"
  - name: "Lavinia Tan"
  - name: "Timothy D. Hackenberg"
    orcid: "0000-0001-5262-1886"
date: last-modified
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: false
    code-tools: true
    embed-resources: true
    fig-width: 7.5
    fig-dpi: 200
execute:
  warning: false
  message: false
  echo: true
  cache: false
---

## Overview

This document reproduces, end to end, the statistical analyses and figures reported in:

> Wan, H., Tan, L., & Hackenberg, T. D. (2026). Behavioral economic analysis of
> pigeons' token accumulation and reinforcer demand in a laboratory-based token
> economy. *Journal of the Experimental Analysis of Behavior, 125*(2), e70095.
> <https://doi.org/10.1002/jeab.70095>

Six pigeons were exposed to a closed token economy in which responses produced
tokens that could be accumulated and later exchanged for food. Across five
phases, one economically relevant variable was manipulated at a time while the
others were held constant (see @tbl-design). Two outcomes are analyzed:

1.  **Token accumulation** — tokens per exchange period — with **binomial**
    multilevel models (tokens out of a 60-token bank).
2.  **Reinforcer demand** — food reinforcers earned per session — with
    **negative binomial** multilevel models.

All models are Bayesian multilevel (hierarchical) models fit with
[`brms`](https://paul-buerkner.github.io/brms/) via Stan. For each phase, the
manipulated predictor is centered and scaled by its standard deviation, and
subject-level random intercepts and slopes are estimated. Effects are summarized
by the posterior **median** (`Estimate`), the posterior **standard deviation**
(`Est.Error`), and the **probability of direction** (`pd`), the share of the
posterior sharing the sign of the median (analogous to a frequentist *p* value,
ranging from .50 to 1.0).

### Data

The dataset is openly available on the Open Science Framework (OSF):
**<https://osf.io/a7523/>** (DOI [10.17605/OSF.IO/A7523](https://doi.org/10.17605/OSF.IO/A7523)).
Download `Data_PigeonEcon.csv` and place it in the `osf/` folder of this
repository (see the project `README`). The file is **trial-level**: one row per
completed trial, plus a priming row (`TrialNum == 0`) at the start of each
session. Session-level demand measures are reconstructed below from the
per-session cumulative totals.

```{r}
#| label: setup
#| results: hide

## ---- Packages -------------------------------------------------------------
library(tidyverse)   # data wrangling + ggplot2
library(here)        # project-relative paths
library(brms)        # Bayesian multilevel models
library(tidybayes)   # posterior tidying (gather_draws, add_epred_draws, median_qi)
library(patchwork)   # combine ggplot panels
library(knitr)       # tables

## ---- Reproducibility ------------------------------------------------------
SEED <- 2026
set.seed(SEED)
options(mc.cores = parallel::detectCores())

## Use cmdstanr if available (as in the published analysis); else fall back.
BACKEND <- if (requireNamespace("cmdstanr", quietly = TRUE)) "cmdstanr" else "rstan"

## Cache compiled model fits here so re-rendering is fast. Refit only when the
## model or data change (this also avoids stale cached fits).
dir.create(here("models"),  showWarnings = FALSE)
dir.create(here("figures"), showWarnings = FALSE)

## Shared plotting aesthetics -------------------------------------------------
col_acc <- "#C0392B"   # red  — token accumulation
col_dem <- "#4C72B0"   # blue — reinforcer demand

theme_pigeon <- function() {
  theme_bw(base_size = 12) +
    theme(
      panel.grid      = element_blank(),
      panel.border    = element_rect(colour = "black", linewidth = 0.8),
      strip.background = element_blank(),
      strip.text      = element_text(face = "bold"),
      axis.title      = element_text(face = "bold"),
      axis.ticks.length = unit(-0.12, "cm"),
      plot.title      = element_text(face = "bold", hjust = 0.5)
    )
}
```

## Data import and preparation

The OSF export uses publication-facing names (`Pigeon`, `Phase`, `TokMag`) and
encodes the phase in which each condition was run as a string. Two conditions
served double duty and belong to two phases at once: the last condition of
Phase 1 was also the first of Phase 2 (`"1 | 2"`), and the last of Phase 4 was
the first of Phase 5 (`"4 | 5"`). Replication conditions are flagged by an `"R"`
suffix on the pigeon ID (e.g., `126R`).

Because the OSF file omits the internal session date, we recover session
boundaries from `TrialNum`, which restarts each session: a new session begins
wherever `TrialNum` does not increase from the previous row (within a pigeon).

```{r}
#| label: import

data_path <- here("osf", "Data_PigeonEcon.csv")

if (!file.exists(data_path)) {
  stop("Data_PigeonEcon.csv not found in osf/.\n",
       "Download it from OSF (https://osf.io/a7523/) and place it in the osf/ folder.")
}

raw <- read_csv(data_path, show_col_types = FALSE)

trials <- raw |>
  mutate(
    Replication = if_else(str_detect(Pigeon, "R$"), 1L, 0L),
    Subject     = factor(str_remove(Pigeon, "R$")),
    Wage        = TokMag,                        # economic analogue: wage
    phase_set   = str_split(Phase, "\\s*\\|\\s*") # e.g., "1 | 2" -> c("1","2")
  ) |>
  group_by(Pigeon) |>
  mutate(Session = cumsum(replace_na(TrialNum <= lag(TrialNum), TRUE))) |>
  ungroup() |>
  mutate(SessionID = paste(Pigeon, Session, sep = "-"))

## Session-level frame for demand: the last row of each session carries that
## session's cumulative totals (TotalRft, TotTokProdResp), and its TrialNum is
## the number of completed trials that session.
sessions <- trials |>
  group_by(SessionID) |>
  slice_max(TrialNum, n = 1, with_ties = FALSE) |>
  ungroup()

## Helper: does a row's phase set contain a given phase code?
in_phase <- function(df, code) map_lgl(df$phase_set, ~ code %in% .x)
```

Each phase's model frame keeps only initial (non-replication) conditions and, for
accumulation, drops the `TrialNum == 0` priming rows. The manipulated predictor
is centered at a fixed reference value and scaled by its standard deviation
*within that frame* (so the accumulation and demand versions of a predictor can
differ, exactly as in the published analysis). Centering shifts only the
intercept, so the reported slopes are unaffected by the choice of reference.

```{r}
#| label: model-frames

## Reference (centering) values and economic labels for each phase.
phase_info <- tribble(
  ~phase, ~var,          ~center, ~economic,                     ~xlab,
  "1",    "TokProdFR",   5,       "Labor / wage (inverse)",      "Token-Production Ratio",
  "2",    "ExchProdFR",  100,     "Transaction cost",            "Exchange-Production Ratio",
  "3",    "Price",       2,       "Price",                       "Token-Exchange Price",
  "4",    "FreeToken",   5,       "Nonlabor income",             "Number of Free Tokens",
  "5",    "Wage",        5,       "Wage (reinforcer magnitude)", "Token-Reinforcement Magnitude"
)

## Build a standardized model frame for one phase.
##   level = "trial"   -> accumulation (trial-level, drop priming rows)
##   level = "session" -> demand (session-level)
model_frame <- function(code, var, center, level = c("trial", "session")) {
  level <- match.arg(level)
  base  <- if (level == "trial") trials else sessions
  out <- base |>
    filter(in_phase(base, code), Replication == 0)
  if (level == "trial") out <- filter(out, TrialNum != 0)
  out |>
    mutate("{var}_c" := (.data[[var]] - center) / sd(.data[[var]])) |>
    select(-phase_set)
}
```

## Statistical models

Two thin wrappers encode the exact model specifications, priors, and sampler
settings from the published analysis, so every phase is fit identically.

- **Accumulation:** `binomial` with a 60-token ceiling,
  `y | trials(60) ~ 1 + x_c + (1 + x_c | Subject)`.
- **Demand:** `negbinomial`, `y ~ 1 + x_c + (1 + x_c | Subject)`. The dispersion
  (`shape`) varies by subject except in Phase 4, where a single population-level
  `shape` is estimated (matching the published models).

Priors are weakly informative Cauchy distributions
(Gelman et al., 2008): `cauchy(0, 10)` on the intercept and `cauchy(0, 5)` on
regression coefficients and variance components. Each model draws 4 chains of
4,000 iterations (2,000 warmup).

```{r}
#| label: model-fitters

## Binomial accumulation model (tokens out of 60).
fit_acc <- function(df, var, outcome = "TokAcc", name) {
  form <- bf(as.formula(sprintf(
    "%s | trials(60) ~ 1 + %s_c + (1 + %s_c | Subject)", outcome, var, var)))
  brm(
    form, data = df, family = binomial(),
    prior = c(prior(cauchy(0, 10), class = Intercept),
              prior(cauchy(0,  5), class = b),
              prior(cauchy(0,  5), class = sd)),
    iter = 4000, warmup = 2000, chains = 4, seed = SEED,
    backend = BACKEND, refresh = 0,
    control = list(adapt_delta = 0.95, max_treedepth = 15),
    file = here("models", name), file_refit = "on_change"
  )
}

## Negative-binomial demand model. shape_by_subject = FALSE reproduces the
## Phase 4 specification (single population-level dispersion).
fit_dem <- function(df, var, outcome = "TotalRft", name, shape_by_subject = TRUE) {
  main <- sprintf("%s ~ 1 + %s_c + (1 + %s_c | Subject)", outcome, var, var)
  if (shape_by_subject) {
    form  <- bf(as.formula(main), shape ~ 1 + (1 | Subject))
    prior <- c(prior(cauchy(0, 10), class = Intercept),
               prior(cauchy(0,  5), class = b),
               prior(cauchy(0,  5), class = sd),
               prior(cauchy(0,  5), class = Intercept, dpar = shape),
               prior(cauchy(0,  5), class = sd,        dpar = shape))
  } else {
    form  <- bf(as.formula(main))
    prior <- c(prior(cauchy(0, 10), class = Intercept),
               prior(cauchy(0,  5), class = b),
               prior(cauchy(0,  5), class = sd),
               prior(cauchy(0,  5), class = shape))
  }
  brm(
    form, data = df, family = negbinomial(),
    prior = prior,
    iter = 4000, warmup = 2000, chains = 4, seed = SEED,
    backend = BACKEND, refresh = 0,
    control = list(adapt_delta = 0.99, max_treedepth = 15),
    file = here("models", name), file_refit = "on_change"
  )
}

## Tidy the population-level slope of a fitted model into one summary row:
## posterior median, SD, and probability of direction. The slope is the single
## population-level coefficient whose name ends in "_c" (b_<var>_c).
slope_summary <- function(model, label, outcome) {
  dd    <- as_draws_df(model)
  term  <- grep("^b_.*_c$", names(dd), value = TRUE)[1]
  draws <- dd[[term]]
  tibble(
    Effect    = label,
    Outcome   = outcome,
    Estimate  = median(draws),
    Est.Error = sd(draws),
    pd        = max(mean(draws > 0), mean(draws < 0))
  )
}
```

> **Note.** The first render fits 14 Bayesian models and can take several minutes.
> Fits are cached under `models/`; subsequent renders reuse them and complete
> quickly. Set `file_refit = "always"` to force a full refit.

### Token accumulation

```{r}
#| label: fit-accumulation

## One standardized frame per phase (trial level).
af <- pmap(phase_info, function(phase, var, center, ...)
  model_frame(phase, var, center, level = "trial")) |>
  set_names(phase_info$phase)

acc1  <- fit_acc(af[["1"]], "TokProdFR",  name = "acc_p1_tokprod")
acc2  <- fit_acc(af[["2"]], "ExchProdFR", name = "acc_p2_exchprod")
acc3  <- fit_acc(af[["3"]], "Price",      name = "acc_p3_price")
acc4  <- fit_acc(af[["4"]], "FreeToken",  name = "acc_p4_freetok")            # total tokens
acc4A <- fit_acc(af[["4"]], "FreeToken",  outcome = "TokProdResp",
                 name = "acc_p4_freetok_earned")                              # earned tokens
acc5  <- fit_acc(af[["5"]], "Wage",       name = "acc_p5_wage")              # total tokens
acc5A <- fit_acc(af[["5"]], "Wage",       outcome = "TokProdResp",
                 name = "acc_p5_wage_resp")                                   # token-production responses
```

```{r}
#| label: tbl-accumulation
#| tbl-cap: "Token accumulation: population-level effects (posterior median, SD, and probability of direction) of each manipulated variable on tokens per exchange."

acc_summary <- bind_rows(
  slope_summary(acc1,  "Phase 1 · Token-production ratio",   "Tokens/exchange"),
  slope_summary(acc2,  "Phase 2 · Exchange-production ratio", "Tokens/exchange"),
  slope_summary(acc3,  "Phase 3 · Token-exchange price",      "Tokens/exchange"),
  slope_summary(acc4,  "Phase 4 · Free tokens",               "Total tokens/exchange"),
  slope_summary(acc4A, "Phase 4 · Free tokens",               "Earned tokens/exchange"),
  slope_summary(acc5,  "Phase 5 · Reinforcement magnitude",   "Total tokens/exchange"),
  slope_summary(acc5A, "Phase 5 · Reinforcement magnitude",   "Token-production responses")
)

acc_summary |>
  mutate(across(c(Estimate, Est.Error, pd), \(x) round(x, 3))) |>
  select(Effect, Outcome, Estimate, Est.Error, pd) |>
  kable(align = "llrrr")
```

### Reinforcer demand

```{r}
#| label: fit-demand

## One standardized frame per phase (session level).
sf <- pmap(phase_info, function(phase, var, center, ...)
  model_frame(phase, var, center, level = "session")) |>
  set_names(phase_info$phase)

dem1  <- fit_dem(sf[["1"]], "TokProdFR",  name = "dem_p1_tokprod")
dem2  <- fit_dem(sf[["2"]], "ExchProdFR", name = "dem_p2_exchprod")
dem3  <- fit_dem(sf[["3"]], "Price",      name = "dem_p3_price")
dem4  <- fit_dem(sf[["4"]], "FreeToken",  name = "dem_p4_freetok",
                 shape_by_subject = FALSE)                                   # total consumption
dem4A <- fit_dem(sf[["4"]], "FreeToken",  outcome = "TotTokProdResp",
                 name = "dem_p4_freetok_earned", shape_by_subject = FALSE)   # earned consumption
dem5  <- fit_dem(sf[["5"]], "Wage",       name = "dem_p5_wage")             # consumption
dem5A <- fit_dem(sf[["5"]], "Wage",       outcome = "TotTokProdResp",
                 name = "dem_p5_wage_resp")                                  # token-production responses
```

```{r}
#| label: tbl-demand
#| tbl-cap: "Reinforcer demand: population-level effects (posterior median, SD, and probability of direction) of each manipulated variable on food reinforcers earned per session."

dem_summary <- bind_rows(
  slope_summary(dem1,  "Phase 1 · Token-production ratio",    "Consumption"),
  slope_summary(dem2,  "Phase 2 · Exchange-production ratio", "Consumption"),
  slope_summary(dem3,  "Phase 3 · Token-exchange price",      "Consumption"),
  slope_summary(dem4,  "Phase 4 · Free tokens",               "Total consumption"),
  slope_summary(dem4A, "Phase 4 · Free tokens",               "Earned consumption"),
  slope_summary(dem5,  "Phase 5 · Reinforcement magnitude",   "Consumption"),
  slope_summary(dem5A, "Phase 5 · Reinforcement magnitude",   "Token-production responses")
)

dem_summary |>
  mutate(across(c(Estimate, Est.Error, pd), \(x) round(x, 3))) |>
  select(Effect, Outcome, Estimate, Est.Error, pd) |>
  kable(align = "llrrr")
```

## Figures

Each panel overlays the model's fitted function (posterior median with a 95%
credible interval, from `add_epred_draws()`) on the observed per-condition means
(±1 *SE*). Open circles connected by a line are initial exposures; open diamonds
are replication conditions. Panels are faceted by pigeon with free *y*-axes.
The model fits are exactly those tabulated above (the models exclude only
replication conditions and priming rows). The published figures additionally
used individually tuned per-pigeon axis limits and a few ad-hoc cosmetic point
adjustments for legibility; those choices are omitted here for clarity and do
not affect any estimate.

```{r}
#| label: figure-helpers

## Posterior fitted curve for one model, back-transformed to the raw predictor.
epred_curve <- function(model, df, var, center) {
  vc <- paste0(var, "_c")
  s  <- sd(df[[var]])
  grid <- expand_grid(
    Subject = unique(df$Subject),
    xc      = seq(min(df[[vc]]), max(df[[vc]]), by = 0.05)
  )
  grid[[vc]] <- grid$xc                 # predictor on the model's centered/scaled scale
  grid$x     <- grid$xc * s + center    # same predictor on the raw scale (for plotting)
  grid |>
    add_epred_draws(model) |>
    group_by(Subject, x) |>
    median_qi(.epred, .width = 0.95) |>
    ungroup()
}

## Observed per-condition summary (mean ± SE) for a phase and outcome.
obs_summary <- function(df, code, var, yvar) {
  df |>
    filter(in_phase(df, code)) |>
    group_by(Subject, Replication, x = .data[[var]]) |>
    summarise(mean = mean(.data[[yvar]]),
              se   = sd(.data[[yvar]]) / sqrt(n()), .groups = "drop")
}

## Standard panel: fitted ribbon + observed means (initial line/points, replication diamonds).
panel_plot <- function(curve, obs, xbreaks, xlab, ylab, colour) {
  init <- filter(obs, Replication == 0)
  rep  <- filter(obs, Replication == 1)
  p <- ggplot() +
    geom_ribbon(data = curve, aes(x, .epred, ymin = .lower, ymax = .upper),
                fill = colour, alpha = 0.25) +
    geom_line(data = init, aes(x, mean), colour = colour, linewidth = 0.8) +
    geom_errorbar(data = init, aes(x, ymin = mean - se, ymax = mean + se),
                  width = 0, colour = colour, linewidth = 0.8) +
    geom_point(data = init, aes(x, mean), shape = 21, fill = "white",
               colour = colour, size = 2.8, stroke = 1.1)
  if (nrow(rep) > 0)
    p <- p + geom_point(data = rep, aes(x, mean), shape = 23, fill = "white",
                        colour = "gray30", size = 2.6, stroke = 1)
  p +
    facet_wrap(~Subject, ncol = 3, scales = "free_y") +
    scale_x_continuous(breaks = xbreaks) +
    labs(x = xlab, y = ylab) +
    theme_pigeon()
}
```

### Figure 3 — Token accumulation vs. token-production ratio, exchange-production ratio, and price

```{r}
#| label: fig-3
#| fig-cap: "Mean tokens per exchange as a function of the token-production ratio (top), exchange-production ratio (middle), and token-exchange price (bottom) for each pigeon."
#| fig-width: 7.5
#| fig-height: 12

f3a <- panel_plot(epred_curve(acc1, af[["1"]], "TokProdFR", 5),
                  obs_summary(trials |> filter(TrialNum != 0), "1", "TokProdFR", "TokAcc"),
                  c(1, 5, 10), "Token-Production Ratio", "Mean Tokens per Exchange", col_acc)
f3b <- panel_plot(epred_curve(acc2, af[["2"]], "ExchProdFR", 100),
                  obs_summary(trials |> filter(TrialNum != 0), "2", "ExchProdFR", "TokAcc"),
                  c(25, 50, 100, 200), "Exchange-Production Ratio", "Mean Tokens per Exchange", col_acc)
f3c <- panel_plot(epred_curve(acc3, af[["3"]], "Price", 2),
                  obs_summary(trials |> filter(TrialNum != 0), "3", "Price", "TokAcc"),
                  c(1, 2, 5), "Token-Exchange Price", "Mean Tokens per Exchange", col_acc)

fig3 <- f3a / f3b / f3c
ggsave(here("figures", "Figure 3.jpg"), fig3, width = 180, height = 360,
       units = "mm", dpi = 300)
fig3
```

### Figure 4 — Token accumulation vs. free tokens and reinforcement magnitude

Panel A adds *earned* tokens (filled points, dashed line = total − free); Panel B
adds token-production *responses* per exchange (filled squares, dashed line).

```{r}
#| label: fig-4
#| fig-cap: "Mean tokens per exchange as a function of the number of free tokens (top) and token-reinforcement magnitude (bottom) for each pigeon."
#| fig-width: 7.5
#| fig-height: 8.5

## Panel A — free tokens: total (ribbon + open circles) and earned (filled, dashed).
earned_tok <- trials |>
  filter(in_phase(trials, "4"), TrialNum != 0, Replication == 0) |>
  group_by(Subject, x = FreeToken) |>
  summarise(earned = mean(TokAcc) - unique(FreeToken), .groups = "drop") |>
  mutate(earned = if_else(x == 0, NA_real_, earned))

f4a <- panel_plot(epred_curve(acc4, af[["4"]], "FreeToken", 5),
                  obs_summary(trials |> filter(TrialNum != 0), "4", "FreeToken", "TokAcc"),
                  c(0, 2, 5, 10), "Number of Free Tokens", "Mean Tokens per Exchange", col_acc) +
  geom_line(data = earned_tok, aes(x, earned), colour = col_acc,
            linewidth = 0.5, linetype = 2, na.rm = TRUE) +
  geom_point(data = earned_tok, aes(x, earned), colour = col_acc, fill = col_acc,
             shape = 21, size = 2.3, na.rm = TRUE)

## Panel B — magnitude: total tokens (ribbon + open circles) and token-production responses.
resp_tok <- trials |>
  filter(in_phase(trials, "5"), TrialNum != 0, Replication == 0) |>
  group_by(Subject, x = Wage) |>
  summarise(resp = mean(TokProdResp), .groups = "drop") |>
  mutate(resp = if_else(x == 1, NA_real_, resp))

f4b <- panel_plot(epred_curve(acc5, af[["5"]], "Wage", 5),
                  obs_summary(trials |> filter(TrialNum != 0), "5", "Wage", "TokAcc"),
                  c(1, 2, 5, 10), "Token-Reinforcement Magnitude", "Mean Tokens per Exchange", col_acc) +
  geom_line(data = resp_tok, aes(x, resp), colour = col_acc,
            linewidth = 0.5, linetype = 2, na.rm = TRUE) +
  geom_point(data = resp_tok, aes(x, resp), colour = col_acc, fill = col_acc,
             shape = 22, size = 2.3, na.rm = TRUE)

fig4 <- f4a / f4b
ggsave(here("figures", "Figure 4.jpg"), fig4, width = 180, height = 245,
       units = "mm", dpi = 300)
fig4
```

### Figure 5 — Demand vs. token-production ratio, exchange-production ratio, and price

```{r}
#| label: fig-5
#| fig-cap: "Total food reinforcers earned as a function of the token-production ratio (top), exchange-production ratio (middle), and token-exchange price (bottom) for each pigeon."
#| fig-width: 7.5
#| fig-height: 12

f5a <- panel_plot(epred_curve(dem1, sf[["1"]], "TokProdFR", 5),
                  obs_summary(sessions, "1", "TokProdFR", "TotalRft"),
                  c(1, 5, 10), "Token-Production Ratio", "Mean Food Consumption", col_dem)
f5b <- panel_plot(epred_curve(dem2, sf[["2"]], "ExchProdFR", 100),
                  obs_summary(sessions, "2", "ExchProdFR", "TotalRft"),
                  c(25, 50, 100, 200), "Exchange-Production Ratio", "Mean Food Consumption", col_dem)
f5c <- panel_plot(epred_curve(dem3, sf[["3"]], "Price", 2),
                  obs_summary(sessions, "3", "Price", "TotalRft"),
                  c(1, 2, 5), "Token-Exchange Price", "Mean Food Consumption", col_dem)

fig5 <- f5a / f5b / f5c
ggsave(here("figures", "Figure 5.jpg"), fig5, width = 180, height = 375,
       units = "mm", dpi = 300)
fig5
```

### Figure 6 — Demand vs. free tokens and reinforcement magnitude

Panel A adds *earned* consumption (filled points, dashed line = total food minus
free-token food); Panel B adds token-production *responses* per session.

```{r}
#| label: fig-6
#| fig-cap: "Total food reinforcers earned as a function of the number of free tokens (top) and token-reinforcement magnitude (bottom) for each pigeon."
#| fig-width: 7.5
#| fig-height: 8.5

## Panel A — free tokens: total (ribbon + open circles) and earned consumption.
earned_con <- sessions |>
  filter(in_phase(sessions, "4"), Replication == 0) |>
  group_by(Subject, x = FreeToken) |>
  summarise(earned = mean(TotalRft - TrialNum * FreeToken), .groups = "drop") |>
  mutate(earned = if_else(x == 0, NA_real_, earned))

f6a <- panel_plot(epred_curve(dem4, sf[["4"]], "FreeToken", 5),
                  obs_summary(sessions, "4", "FreeToken", "TotalRft"),
                  c(0, 2, 5, 10), "Number of Free Tokens", "Mean Food Consumption", col_dem) +
  geom_line(data = earned_con, aes(x, earned), colour = col_dem,
            linewidth = 0.5, linetype = 2, na.rm = TRUE) +
  geom_point(data = earned_con, aes(x, earned), colour = col_dem, fill = col_dem,
             shape = 21, size = 2.3, na.rm = TRUE)

## Panel B — magnitude: consumption (ribbon + open circles) and token-production responses.
resp_con <- sessions |>
  filter(in_phase(sessions, "5"), Replication == 0) |>
  group_by(Subject, x = Wage) |>
  summarise(resp = mean(TotTokProdResp), .groups = "drop") |>
  mutate(resp = if_else(x == 1, NA_real_, resp))

f6b <- panel_plot(epred_curve(dem5, sf[["5"]], "Wage", 5),
                  obs_summary(sessions, "5", "Wage", "TotalRft"),
                  c(1, 2, 5, 10), "Token-Reinforcement Magnitude", "Mean Food Consumption", col_dem) +
  geom_line(data = resp_con, aes(x, resp), colour = col_dem,
            linewidth = 0.5, linetype = 2, na.rm = TRUE) +
  geom_point(data = resp_con, aes(x, resp), colour = col_dem, fill = col_dem,
             shape = 22, size = 2.3, na.rm = TRUE)

fig6 <- f6a / f6b
ggsave(here("figures", "Figure 6.jpg"), fig6, width = 180, height = 255,
       units = "mm", dpi = 300)
fig6
```

## Tables

### Table 1 — Experimental variables and their economic analogues

```{r}
#| label: tbl-design
#| tbl-cap: "Key experimental terms, their economic analogues, and definitions."

tribble(
  ~`Experimental term`,            ~`Economic analogy`,          ~`Definition in this study`,
  "Token-production ratio",        "Labor / wage (inverse)",     "Responses (pecks) required to earn one token.",
  "Exchange-production ratio",     "Transaction cost",           "Responses (pecks) required to initiate an exchange period.",
  "Token-exchange price",          "Price / purchase cost",      "Tokens required to exchange for one unit of food.",
  "Free tokens",                   "Nonlabor income / subsidy",  "Unearned tokens provided at the start of each trial.",
  "Token-reinforcement magnitude", "Wage",                       "Tokens earned for completing one token-production requirement."
) |>
  kable()
```

### Appendix Table A1 — Mean performance by condition

Per-condition means over the final five sessions, reconstructed from the OSF
data. Columns follow the published Appendix: mean number of trials, total
token-production / exchange-production / token-exchange responses, food
reinforcers earned, and the food obtained per exchange (`Acc = Rft / trials`).

```{r}
#| label: tbl-appendix
#| tbl-cap: "Reconstructed Appendix Table A1: mean performance measures by pigeon and condition."

## Session-level totals per condition (includes replication conditions, tagged "R").
per_session <- sessions |>
  transmute(
    Pigeon, Phase, TokProdFR, ExchProdFR, TEPrice = Price, Free = FreeToken,
    TokMag, TrialNum,
    TPResp = TotTokProdResp, EPResp = TotExchProdResp, TEResp = TotTokExchResp,
    Rft = TotalRft
  )

appendix_A1 <- per_session |>
  group_by(Pigeon, Phase, TPFR = TokProdFR, EPFR = ExchProdFR,
           TEPrice, Free, TokMag) |>
  summarise(
    TrialNum = mean(TrialNum), TPResp = mean(TPResp), EPResp = mean(EPResp),
    TEResp = mean(TEResp), Rft = mean(Rft), .groups = "drop"
  ) |>
  mutate(Acc = Rft / TrialNum) |>
  arrange(Pigeon, Phase) |>
  mutate(across(where(is.numeric), \(x) round(x, 1)))

write_csv(appendix_A1, here("figures", "Appendix_Table_A1.csv"))
kable(appendix_A1)
```

## Reproducibility

```{r}
#| label: session-info
sessionInfo()
```

## References

- Bürkner, P.-C. (2017). brms: An R package for Bayesian multilevel models using
  Stan. *Journal of Statistical Software, 80*(1), 1–28.
- Carpenter, B., et al. (2017). Stan: A probabilistic programming language.
  *Journal of Statistical Software, 76*(1).
- Gelman, A., Jakulin, A., Pittau, M. G., & Su, Y.-S. (2008). A weakly
  informative default prior distribution for logistic and other regression
  models. *The Annals of Applied Statistics, 2*(4), 1360–1383.
- Wan, H., Tan, L., & Hackenberg, T. D. (2026). Behavioral economic analysis of
  pigeons' token accumulation and reinforcer demand in a laboratory-based token
  economy. *Journal of the Experimental Analysis of Behavior, 125*(2), e70095.
  <https://doi.org/10.1002/jeab.70095>
